%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Freelance (Part-Time)} % Organization
    {Remote} % Location
    {Jun. 2024 - Dec. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed reusable UI component libraries and implemented pages for a domain registrar application and cashback reward frontend based on Figma designs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {555 Comic} % Organization
    {Tokyo, Japan (Remote)} % Location
    {Oct. 2022 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Converted a hybrid codebase with React, and non-React code into a full React application to remove incompatibility issues.}
        \item {Implemented new features using React and Kalidokit for body part tracking, enabling users to pose and generate character images.}
        \item {Technologies: TypeScript, JavaScript, React, Kalidokit (for motion tracking).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contract Software Engineer} % Job title
    {Vox Asia Sdn. Bhd.} % Organization
    {Kuala Lumpur, Malaysia (Remote)} % Location
    {May. 2022 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Python library for social media text formatting, enabling cross-platform compatibility and reducing formatting time.}
        \item {Technologies: Python, Markdown}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Vox Asia Sdn. Bhd.} % Organization
    {Kuala Lumpur, Malaysia (Remote)} % Location
    {Feb. 2021 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Django-based REST API for an AI-powered F\&B chatbot.}
        \item {Led deployment using Docker and Kubernetes on AWS under tight deadlines.}
        \item {Provided mentorship to junior developers on technical challenges.}
        \item {Technologies: Python, Django, Docker, Kubernetes, PostgreSQL}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer, Backend Department} % Job title
    {Deriv Services Sdn. Bhd.} % Organization
    {Cyberjaya, Selangor, Malaysia} % Location
    {Jun. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built an automated payment processing service to streamline financial operations, reducing manual workload by automating payments based on predefined rules.}
        \item {Gained proficiency in Perl5 and contributed to a complex microservices architecture with minimal documentation.}
        \item {Technologies: Perl5, Node.js, Hapi.dev, PostgreSQL, Docker, CI/CD (Travis).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer, Frontend Department} % Job title
    {Deriv Services Sdn. Bhd.} % Organization
    {Cyberjaya, Selangor, Malaysia} % Location
    {Dec. 2018 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to the development of Deriv Trader, a real-time options trading application, by building core UI components (e.g., buttons, dropdowns, modals, tooltips) using React and TypeScript.}
        \item {Implemented a Canvas Draw Queue Manager to manage layering and rendering of chart components, ensuring proper marker placement and event handling.}
        \item {Integrated SendBird API for a P2P chat feature, overcoming challenges with React and non-React JS compatibility using iFrames and PostMessage.}
        \item {Collaborated with UI/UX and compliance teams to ensure regulatory adherence and seamless user experiences.}
        \item {Technologies: TypeScript, JavaScript, React, RxJS, WebSockets, LESS/SASS/BEM, Docker, CI/CD.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Project Based} % Job title
    {Freelance} % Organization
    {Malaysia} % Location
    {Jul. 2017 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a REST API for an “Over-The-Counter Payment Tracker” using Django REST Framework, collaborating with an in-house front-end developer.}
        \item {Developed landing pages for local businesses and customized Shopify templates, e.g one for Smart Manufacturing Exhibition 2018.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
