%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Notable Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Commercial Project} % Job title
    {Deriv Trader} % Organization
    {Deriv Sdn. Bhd.} % Location
    {Dec. 2018 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A trading application used to provide clients with options trading functionality. It's a websocket, event based React application with a custom charting library. The application is a rewrite of an older application named SmartTrader.}
        \item {Contributed in the rewrite effort. Responsibilities include implementing pixel-perfect code based on designs given by UI/UX team, and implementing existing features from SmartTrader.}
        \item {Developed a system to implement raw canvas components in the charting library with a layering system to make sure components are drawn in proper order. This makes it possible for the canvas to respond to React events.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Commercial Project} % Job title
    {Automated Payment Processing Service} % Organization
    {Deriv Sdn. Bhd.} % Location
    {June. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {An internal payment processing service that automates certain payments processes. For example, automatically approve refunds under \$5.}
        \item {Participated in designing the API, and database.}
        \item {Developed major parts of the system including the APIs, tests, and CI/CD pipeline for automated testing and deployment.}
        \item {Built it in the course of 4 months in a team of 4 using NodeJS (TypeScript, Hapi.dev), PostgreSQL, and Docker.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Personal Project} % Job title
    {asanitize} % Organization
    {Open Source} % Location
    {May. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {A simple commandline tool to bulk delete messages/posts from social media accounts.}
          \item {Reversed engineered Discord's user API because official API is only for bots.}
          \item {Implemented a custom Discord user API library in the application and hooked it up to business logic.}
          \item {Written in Python, and repository is at: https://github.com/gohanko/asanitize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Final Year Project} % Job title
    {Datarice} % Organization
    {University Tunku Abdul Rahman} % Location
    {Mar. 2023 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {A real time IOT data visualisation and debugging tool written in Typescript, and NextJS.}
          \item {Implemented function to display data in real time using websockets, and ability to read files and update the charts as data comes in.}
          \item {Repository: https://github.com/gohanko/datarice}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {University Course Project} % Job title
    {SidewayQR REST API \& Android App} % Organization
    {University Tunku Abdul Rahman} % Location
    {Jul. 2024 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Backend REST API and Android application for a QR attendance scanning software.}
          \item {REST API built using Typescript, Express, and sequelize (an ORM library). Responsible for providing QR attendance functionalities (QR scanning, QR display, etc).}
          \item {Android application built using Kotlin, Jetpack Compose, and Material 3. It's an implementation to provide the functionalities to the user.}
          \item {REST API and Android app repositories: https://github.com/gohanko/sidewayqr-api and https://github.com/gohanko/SidewayQR.}
      \end{cvitems}
    }

\end{cventries}